A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-03-16 paper/theor-experiment.tex
putting in first figure

The design variables include both solenoid current, IBF and IM,
the gun phase, GPHASE, and the laser full width half maximum in 
the longitudinal direction. The definition of the design variables 
was included in the OPAL input file:
\vspace{0.2cm}
{\footnotesize \begin{verbatim}
// Gun variables
dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=350.0, UPPERBOUND=500.0;
dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;

@@

OPAL-T was used as the forward solver, and a study on time step and 
number of particles was done to reduce the time to simulation while 
maintaining the physics of interest. We choose ten thousand particles 
in combination with adjusting the time step near sensitive elements (i.e. quadurpoles). 
The resulting simulations are low fidelity, but closely approximate 
the mid fidelity simulations for metrics of interest, as shown in Fig. \ref{tstep}.
\begin{figure}\ref{tstep}
	\centering
	%\includegraphics[width=0.8\linewidth]{Report/}
	\caption{Comparison of different fidelity models.}
	\label{tstep}
\end{figure}

As in Section \ref{ferrario}, 
we also have to define several beam line parameters that 
are not included in the optimization design variables above.
These

>>>>

The design variables include both solenoid current, IBF and IM,
the gun phase, GPHASE, and the laser full width half maximum in 
the longitudinal direction. The definition of the design variables 
was included in the OPAL input file, 
As in Section \ref{ferrario}, 
we also have to define several beam line parameters that 
are not included in the optimization design variables above.
These are shown in Table \ref{awatable}.

\begin{align}
\text{min}  \quad & \text{rms}_{x, s1}, \quad \text{rms}_{x, s2} \label{eq:awa:p1}\\
& \text{rms}_{s, s1}, \quad \text{rms}_{s, s2} \label{eq:awa:p2}\\
& \varepsilon_{x,s1}, \quad \varepsilon_{x,s2} \label{eq:awa:p3} \\
\text{subject to} \quad & q = 200 \left[\text{pC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{RF}} = 100 \left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \sigma_{L} \leq \sigma_x = \sigma_y \leq \sigma_{U} \label{eq:awa:firstdvar}\\
\quad & \text{KS}_{L} \leq \text{KS}_{\text{RF}} \leq \text{KS}_{U} \label{eq:awa:seconddvar}\\
\quad & \text{LAG}_{L} \leq \text{LAG}_{\text{RF}} \leq \text{LAG}_{U} \\
\quad & \Delta z_{L\text{KS}} \leq \Delta z_{\text{KS}} \leq \Delta z_{U\text{KS}} \label{eq:awa:lastdvar}
\end{align}

\vspace{0.2cm}
{\footnotesize \begin{verbatim}
// Gun variables
dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=350.0, UPPERBOUND=500.0;
dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;

@@

OPAL-T was used as the forward solver, and a study on time step and 
number of particles was done to reduce the time to simulation while 
maintaining the physics of interest. All jobs were run and compared 
on 8 cores to take advantage of the KNL, by running 8 jobs per node.
After comparing several options we choose ten thousand particles 
in combination with adjusting the time step near sensitive elements 
(i.e. quadurpoles, dipole). 
The resulting simulations are low fidelity, but closely approximate 
the mid fidelity simulations for metrics of interest, as shown in 
Fig. \ref{tstep}.

\begin{table}[h!]
	\begin{center}
		\caption{Low and mid fidelity simulation parameters.}
		\label{fidelity}
		\begin{tabular}{l ccc}
			\hline\noalign{\smallskip}
			 & Number of particles & Time step (seconds) & Time to simulation (minutes)\\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			low fidelity  			&  10,000   & $5 \times10^{-11}$  &  2.6 \\
			mid fidelity 			&  100,000  & $1 \times 10^{-12}$ &  \\
			adjusted low fidelity  	&  10,000   & $2 \times 10^{-12}$, $1 \times 10^{-11}$ & 1.5 \\
			\noalign{\smallskip}\hline
		\end{tabular}
	\end{center}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{Report/timestep_comparison}
	\caption{Comparison of different fidelity models.}
	\label{tstep}
\end{figure}
